Developing a Bubble Chamber Particle Discriminator Using Semi-Supervised Learning

### 2018-08-30 documentation/paper.tex
Removed graphs with accuracy by hyper

As seen in Figure \ref{grav_acc_by_hyper}, all three hyperparameters that were optimized during the grid search had a significant effect on accuracy:

\begin{itemize}
    \item Smaller gravitational multipliers improved performance; the best value tested was 0.0005. This implies that the gravity effect on each unlabeled event should be weighted lightly compared to the labeled examples.
    \item Higher learning rates improve performance, with the best value tested at a quite high 0.03.
    \item Larger distortion powers (which raise the confidence threshold for a significant gravitational effect) improved performance, with the best tested at 11.
\end{itemize}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{grav_acc_by_hyper}
    \caption{\label{grav_acc_by_hyper} Accuracy of gravitational differentiation as a function of hyperparameter values.}
\end{figure}

@@

During a grid search of these parameters (in addition to regularization parameters of the network), the best mean accuracy over three runs of an individual configuration was 99\%, using 256 initial labeled examples in $\varsigma$. With 128 examples, the maximum was 98\%; with 64 it was 97\%, and with 32 95\%. From this, it is evident that it is possible to achieve very high accuracy using this technique. It is also clear that, in general, larger initial sets produce higher performance.

@@

THIS NEEDS TO BE EDITED VVVV

Digging deeper into the performance throughout the runs of the grid search, Figure \ref{icn_acc_by_hyper} shows the mean accuracy as a function of each of the hyperparameters that were optimized. Dropout has a clear effect, with 25\% shown to be the optimal number of neurons to drop. L2 regularization is also significant; all $\lambda$ values greater than 0 make performance worse.

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{icn_acc_by_hyper}
    \caption{\label{icn_acc_by_hyper} Mean accuracy of iterative cluster nucleation as a function of hyperparameter values.}
\end{figure}

>>>>

@@

@@

During a grid search of these parameters (in addition to regularization parameters of the network), the best mean accuracy over three runs of an individual configuration was 99\%, using 256 initial labeled examples in $\varsigma$. With 128 examples, the maximum was 98\%; with 64 it was 97\%; and with 32, 95\%. From this, it is evident that it is possible to achieve very high accuracy using this technique. It is also clear that, in general, larger initial sets produce higher performance.

@@
